\item {[}ALVL/2019/P2/10{]} 

In this question you should state the parameters of any normal distributions
you use.

A company makes 3-legged wooden stools from 4 solid components - a
seat in the form of a disc, and 3 legs each in the form of a long,
thin cylinder. The seats and legs are bought in bulk from another

company. Over a period of time it is found that the masses of the
seats are normally distributed; 80\% of the seats have mass less than
2.1 kg, and 15\% of the seats have mass less than 1.95 kg. 
\begin{enumerate}
\item Find the mean mass of the seats and show that the standard deviation
is 0.0799 kg, correct to 3 significant figures. \hfill{} {[}3{]}
\end{enumerate}
The masses of the legs, in kg, follow the distribution $N\left(1.2,0.02^{2}\right)$. 
\begin{enumerate}
\item Find the expected number of legs with mass more than 1.21 kg in a
randomly chosen batch of 500 legs. \hfill{}{[}2{]}
\item Find the probability that the total mass of a randomly chosen seat
and 3 randomly chosen legs is between 5.6 kg and 5.7 kg. \hfill{}
{[}3{]}
\end{enumerate}
In order to make the stools, circular holes are drilled in the seats
and the legs are fitted into them. In this process, the mass of seats
is modelled as being reduced by 9\% and the masses of the legs are

unchanged. 
\begin{enumerate}
\item Find the probability that the total mass of a randomly chosen drilled
seat and 3 randomly chosen legs is less than 5.6 kg. \hfill{} {[}3{]}
\end{enumerate}
The holes made in the seats have diameters, in mm, that follow the
distribution $N\left(31,0.4^{2}\right)$ and the diameters of the
legs, in mm, follow the distribution $N\left(30.7,0.3^{2}\right)$
. If the diameter of a leg is greater

than the diameter of a hole, then the leg has to be sanded down to
make it fit. If the diameter of a hole is more than 0.8 mm greater
than the diameter of a leg, then padding has to be added when the
leg is

glued to the seat.
\begin{enumerate}
\item A steel is made of a randomly chosen drilled seat and 3 randomly chosen
legs. The legs are paired up with the holes at random. Find the probability
that the 3 legs can be fitted without the need for any sanding or
padding. \hfill{}{[}4{]}
\end{enumerate}
