\item {[}ALVL/2016/P2/6{]}

The number of employees of a company, classified by department and
gender, is shown below. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline 
 & Production & Development & Administration & Finance\tabularnewline
\hline 
Male & 2345 & 1013 & 237 & 344\tabularnewline
\hline 
Female & 867 & 679 & 591 & 523\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item The directors wish to sunrey a sample of 100 of the employees. This
sample is to be a stratified sample, based on department and gender. 
\begin{enumerate}
\item How many males should be in the sample? \hfill{} {[}1{]}
\item How many females from the Development department should be in the
sample? \hfill{} {[}1{]}
\end{enumerate}
\end{enumerate}
The Managing Director knows that, some years ago. the mean age of
employees was 37 years. He believes that the mean age of employees
now is less than 37 years.
\begin{enumerate}
\item State why the stratified sample from part (i) should not be used for
a hypothesis test of the Managing Director\textquoteright s belief.
\hfill{} {[}1{]}
\end{enumerate}
The Company Secretary obtains a suitable sample of 80 employees in
order to carry out a hypothesis test of the Managing Director\textquoteright s
belief that the mean age of the employees now is less than 37 years.
You are given that the population variance of the ages is 140 years.
\begin{enumerate}
\item Write down appropriate hypotheses to test the Managing Director\textquoteright s
belief. You are given that the result of the test, using a 5\% significance
level, is that the Managing Director's belief should be accepted.
Determine the set of possible values of the mean age of the sample
of employees. \hfill{} {[}4{]}
\item You are given instead that the mean age of the sample of employees
is 35.2 years, and that the result of a test at the $\alpha$\% significance
level is that the Managing Director\textquoteleft s belief should
not be accepted. Find the set of possible values of $\alpha$. \hfill{}
{[}3{]}
\end{enumerate}
