\item {[}ALVL/2016/P2/10{]}

Mia owns a field. Various types of weed are found in Mia's field. 
\begin{enumerate}
\item State, in this context, two conditions that must be met for the numbers
of a particular type of weed in Mia's field to be well modelled by
a Poisson distribution. \hfill{} {[}2{]}
\end{enumerate}
For the remainder of this question assume that these conditions are
met. There is an average of 1.5 dandelion plants (a type of weed)
per $\mathrm{m}^{2}$ in Mia\textquoteright s field.
\begin{enumerate}
\item Find the probability that in l$\mathrm{m}^{2}$ of Mia\textquoteleft s
field there are at least 2 dandelion plants. \hfill{} {[}2{]}
\item Find the probability that in 4$\mathrm{m}^{2}$ of Mia\textquoteright s
field there are at most 3 dandelion plants. \hfill{}{[}2{]}
\item Use a suitable approximation, which should be stated, to find the
probability that the number of dandelion plants in an 80$\mathrm{m}^{2}$
area of Mia\textquoteright s field is between 110 and 140 inclusive.
\hfill{} {[}4{]}
\end{enumerate}
The distribution of daisies (another type of weed) per $\mathrm{m}^{2}$
in Mia\textquoteright s field can be modelled by $Po\left(\lambda\right)$.
The probability that the number of daisies in a l$\mathrm{m}^{2}$
area of the field is less than or equal to 2 is the same as the probability
that the number of daisies in a 2$\mathrm{m}^{2}$ area of the field
is more than 2.
\begin{enumerate}
\item Write down an equation in $\lambda$ and solve it to find $\lambda$.
\hfill{}{[}4{]}
\end{enumerate}
