\item {[}ALVL/2018/P2/9{]}

Many electronic devices need a fan to keep them cool. In order to
maximise the lifetime of such fans, the speed they run at is reduced
when conditions allow. Running a fan at a lower speed reduces the
power required. The following table gives details, for a particular
type of fan, of the power required ($P$ watts) at different fan speeds
($R$ revolutions per minute).
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline 
Fan speed ($R$) & 3600 & 4500 & 5400 & 6300 & 7200 & 8100 & 9000 & 9900\tabularnewline
\hline 
Power ($P$) & 0.22 & 0.34 & 0.52 & 0.78 & 1.06 & 1.48 & 2.04 & 2.64\tabularnewline
\hline 
\end{tabular} 
\par\end{center}
\begin{enumerate}
\item Draw a scatter diagram of these data. Use your diagram to explain
whether the relationship between $P$ and $R$ is likely to be well
modelled by an equation of the form $P=aR+b$, where $a$ and $b$
are constants.\hfill{} {[}2{]}
\item By calculating the relevant product moment correlation eoefiicients.
determine whether the relationship between $P$ and $R$ is modelled
better by $P=aR+b$ or by $P=aR^{2}+b$. Explain how you decide which
model is better, and state the equation in this case.\hfill{} {[}5{]}
\item Use your equation to estimate the speed of the fan when the power
is 0.9 watts. Explain whether your estimate is reliable.\hfill{}
{[}2{]}
\item Use your equation to estimate the power used when the speed of the
fan is 3300 revolutions per minute. Explain whether your estimate
is reliable. \hfill{}{[}2{]}
\item Re-write your equation from pan (ii) so that it can be used when the
speed of the fan, $R$, is given in revolutions per second. \hfill{}{[}1{]}
\end{enumerate}
