\item {[}ALVL/2019/P2/11{]} 

A company manufactures a wide variety of components for use in domestic
appliances. 
\begin{enumerate}
\item The company introduces a new type of light fitting for refrigerators.
Each day a supervisor selects a sample of 100 of the light fittings
for testing. 
\begin{enumerate}
\item How should the light fittings be selected? Give a reason for this
method of selection. \hfill{} {[}2{]}
\end{enumerate}
The supervisor records the number of faulty light fittings found on
each of 150 working days. Her results are shown in the table. 
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline 
Number faulty & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 or more\tabularnewline
\hline 
Number of days & 4 & 19 & 38 & 41 & 22 & 16 & 6 & 4 & 0\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item Use the information in the table to estimate $p$, the probability
that a light fitting is faulty. \hfill{} {[}1{]}
\item Assuming that the number of faulty fittings found each day follows
the binomial distribution $B\left(100,p\right)$, find the expected
number of days on which 3 faulty fittings are found in a period of
150 working days. \hfill{}{[}2{]}
\end{enumerate}
\item The company also makes heating elements for electric ovens. A fixed
number of randomly chosen heating elements are tested each day and
the number found to be faulty is denoted by $X$.
\begin{enumerate}
\item State, in context, two assumptions neededfor $X$ to be well modelled
by a binomial distribution. \hfill{}{[}2{]}
\end{enumerate}
Assume now that $X$ has the distribution $B\left(80,0.02\right)$. 
\begin{enumerate}
\item Find the probability that, on a randomly chosen day, the number of
elements found to be faulty is between 1 and 4 inclusive. \hfill{}{[}2{]}
\item Find the probability that, in a randomly chosen 5-day working week,
more than 3 elements are found to be faulty on at least 2 days. \hfill{}{[}3{]}
\item Find the probability that, in a randomly chosen 5-day working week,
no more than 8 faulty elements are found in total. \hfill{} {[}2{]}
\end{enumerate}
\end{enumerate}
