\item {[}ALVL/2020/P2/10{]}

Carbon steel is made by adding carbon to iron; this makes the iron
stronger. though less flexible. A steel manufacturing company makes
carbon steel in the form of round bars. The process is designed to
manufacture bars in which the amount of carbon in each bar, by weight.
is 1.5\%. it is known that the percentage of carbon in the steel bars
is distributed normally. and that the standard deviation is 0.09\%.
After comments from customers, the production manager wishes to test,
at the 5\% level of significance. if the percentage of carbon in the
steel bars is. in fact. 1.5\%. He examines a random sample of 15 bars
to determine the percentage of carbon in each bar.
\begin{enumerate}
\item Find the critical region for this test. \hfill{}{[}4{]}
\end{enumerate}
The company recently launched a new line of flat bars made from mild
steel. In mild steel the amount of carbon in each bar, by weight,
is 0.25\%.

Comments front customers suggest that these bars are not sufiiciently
flexible, which makes the production manager suspect that too much
carbon has been added. He decides to perform a hypothesis test on
a random sample of 40 of the new flat bars to find out if this is
the case. 
\begin{enumerate}
\item Explain why the production manager takes a sample of 40 flat bars
for this test when he only took a sample of 15 round bars in his earlier
test.\hfill{} {[}2{]}
\end{enumerate}
The amounts of carbon, $x$\%, in a random sample of 40 flat bars
are summarised as follows. 
\[
n=40\,\,\sum x=10.16\,\,\sum x^{2}=2.586342
\]

\begin{enumerate}
\item Calculate unbiased estimates of the population mean and variance for
the percentage amount of carbon in the flat bars. \hfill{}{[}2{]}
\item Test, at the $2\frac{1}{2}$\% level of significance, whether the
mean amount of carbon in the flat bars is more than 0.25\%. You should
state your hypotheses and define any symbols that you use. \hfill{}{[}5{]}
\end{enumerate}
