\item {[}ALVL/2022/P2/11{]}

Zhou and Tan are both keen amateur swimmers. and several times each
week they compete against each other to see who can swim 100 metres
freestyle in the shortest time. Over a long period, Zhou's times,
in seconds have followed the distribution $N(80,2^{2})$ and Tan's
the distribution $N\left(79,3^{2}\right)$. It is assumed that these
two distributions are independent.
\begin{enumerate}
\item Find the probability that Zhoa wins a randomly chosen race. {[}3{]}
\end{enumerate}
Tan moves abroad for 2 years so the regular races are suspended. Zhou
starts an exercise regime that he believes will reduce his times.
After he has been exercising for a year, he records his time, $x$
seconds, for a random sample of swims. These times are summarised
below. 
\begin{center}
$\begin{array}{ccccc}
n=30 &  & \sum x=2376.3 &  & \sum x^{2}=188653.7\end{array}$
\par\end{center}
\begin{enumerate}
\item[(b)]  Calculate unbiased estimates of the population mean and variance
for Zhou's times afler his exercise regime. \hfill{}{[}2{]}
\item[(c)]  State hypotheses that can he used to test it if Zhou's times have
reduced, defining any symbols you use. Work out the test statistic
in this case, and use it to carry out the test at 5\% level of significance,
giving your conclusion in the context of the question. \hfill{}{[}5{]}
\end{enumerate}
While he is away Tan switches to a high protein diet and wonders whether
this will affect the tunes he takes for his swims. After a year Tan
decides to test, at the 2.5\% level of significance, whether his mean
time has changed. He records a random sample of 6 times and calculates
the mean of these times.
\begin{enumerate}
\item[(d)]  Explain whether Tan should use a l-tail ora 2-tail test.\hfill{}
{[}1{]}
\item[(e)]  Tan makes two assumptions and is then able to carry out his test.
State these two assumptions. \hfill{}{[}2{]}
\end{enumerate}
