\item {[}ALVL/2013/P2/10{]}
\begin{enumerate}
\item Sketch a scatter diagram that might be expected when $x$ and $y$
are related approximately as given to each of the cases (A), (B) and
(C) below. In each case your diagram should include 6 points, approximately
equally spaced with respect to $x$, and with all $x$- and $y$-values
positive. The letters $a$, $b$, $c$, $d$, $e$ and $f$ represent
constants. 
\begin{enumerate}
\item $y=a+bx^{2}$, where $a$ is positive and $b$ is negative, 
\item $y=c+d\ln x$, where $c$ is positive and $d$ is negative,
\item $y=e+\frac{f}{x}$, where $e$ is positive and $f$ is negative. \hfill{}{[}3{]}
\end{enumerate}
A motoring website gives the following information about the distance
travelled, $y$ km, by a certain type of car at different speeds,
$x$ km h$^{-1}$ , on a fixed amount of fuel. 
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Speed, $x$ & 88 & 96 & 104 & 112 & 120 & 128\tabularnewline
\hline 
Distance, $y$ & 148 & 147 & 144 & 138 & 126 & 107\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item Draw the scatter diagram for these values. labelling the axes. \hfill{}{[}1{]}
\item Explain which of the three cases in part (i) is the most appropriate
for modelling these values, and calculate the product moment correlation
coefficient for this case. \hfill{}{[}2{]}
\item It is required to estimate the distance travelled at a speed of 110
km h$^{-1}$. Use the case that you identified in part (iii) to find
the equation of a suitable regression line. and use your equation
to find the required estimate. \hfill{} {[}3{]}
\end{enumerate}
\end{enumerate}
