\item {[}ALVL/2016/P2/8{]}

A website about electric motors gives information about the percentage
efficiency of motors depending on their power, measured in horsepower.
Xian has copied the following table for a particular type of electric
motor, but he has copied one of the efiiciency values wrongly.
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline 
Power, $x$ & 1 & 1.5 & 2 & 3 & 5 & 7.5 & 10 & 20 & 30 & 40 & 50\tabularnewline
\hline 
Efficiency, $y\%$ & 72.5 & 82.5 & 84.0 & 87.4 & 87.5 & 88.5 & 89.5 & 90.2 & 91.0 & 91.7 & 92.4\tabularnewline
\hline 
\end{tabular}
\par\end{center}
\begin{enumerate}
\item Plot a scatter diagram on graph paper for these values, labelling
the axes, using a scale of 2 cm to represent 10\% efficiency on the
$y$-axis and an appropriate scale for the $x$-axis. On your diagram,
circle the point that Xian has copied wrongly. \hfill{}{[}2{]}
\end{enumerate}
For parts (ii), (iii) and (iv) of this question you should \textbf{exclude}
the point for which Xian has copied the efficiency value wrongly.
\begin{enumerate}
\item Explain from your scatter diagram why the relationship between $x$
and $y$ should not be modelled by an equation of the form $y=ax+b$.
\hfill{}{[}1{]}
\item Suppose that the relationship between $x$ and $y$ is modelled by
an equation of the form $y=\frac{c}{x}+d$, where $c$ and $d$ are
constants. State with a reason whether each of $c$ and $d$ is positive
or negative. \hfill{}{[}2{]}
\item Find the product moment correlation coefficient and the constants
$c$ and $d$ for the model in part (iii). \hfill{}{[}3{]}
\item Use the model $y=\frac{c}{x}+d$, with the values of $c$ and $d$
found in part (iv), to estimate the efficiency value ($y$) that Xian
has cepied wrongly. Give two reasons why you would expect this estimate
to be reliable. \hfill{}{[}3{]}
\end{enumerate}
