\item {[}ALVL/2022/P2/10{]}

Adriana is investigating how the prices ol\textasciitilde{} used cars
depend on the distances the cars have been drwen. She collects some
information from a UK website about 7 cars, all of the same make and
model. This is given in the table below, the distance $d$, is in
miles and the price, $p$, in pounds sterling.
\noindent \begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline 
$d$ & 14588 & 8954 & 24030 & 37551 & 45452 & 30100 & 5055\tabularnewline
\hline 
$p$ & 12450 & 15200 & 11900 & 10700 & 10600 & 10900 & 22500\tabularnewline
\hline 
\end{tabular}
\par\end{center}

A scatter diagram for the data is shown below. 
\noindent \begin{center}
<INSERT DIAGRAM HERE>
\par\end{center}

The product moment correlation coefficient between $d$ and $p$ is
$-0.78$. 
\begin{enumerate}
\item What conclusion should Adriana reach about the relationship between
$d$ and $p$? Justify your answer. \hfill{}{[}2{]}
\item Explain whether the product moment correlation coefficient would differ
if Adriana converted the distances to kilometres and the prices to
Singapore dollars. {[}1 mile = 1.6 kilometres; 1 pound sterling =
1.7 Singapore dollars{]}\hfill{} {[}1{]}
\end{enumerate}
Adriana \textquotedbl checks the original information. She realises
that the car with $d=5055$ and$p=22500$ was a special version of
the model, with a bigger engine and many extra features.
\begin{enumerate}
\item[(c)]  Explain why the data relating to this special car should not be
used in any analysis of the data. \hfill{}{[}1{]}
\end{enumerate}
\textbf{In the rest of this question you should not include the data
for this special car.}
\begin{enumerate}
\item[(d)]  Using a reciprocal transformation sketch a scatter diagram for $p$
against $\frac{10000}{d}$. Draw, by eye, a line of best fit on your
scatter diagram.\hfill{} {[}2{]}
\item[(e)]  Show the scatter diagram in part (d) the distances which are used
in drawing the least squares regression line of $p$ on $\frac{100000}{d}$.
Explain why these distances are squared. and why this is referred
to as the \textquoteleft method of least squares'. \hfill{}{[}3{]}
\item[(f)]  Use your calculator to find the equation of the least squares regression
line of $p$ on $\frac{100000}{d}$ and the value of the corresponding
product moment correlauon coefficient. \hfill{}{[}3{]}
\item[(g)]  Use your equation to estimate the price of a car of this make and
model that has travelled 5055 miles. Explain whether you would expect
this estimate to be reliable. \hfill{}{[}2{]}
\end{enumerate}
